---
title: 'Lab 7 Part 1: stringr'
author: "Roupen Khanjian"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

### Detect string patterns with `str_detect()`


```{r}

vec <- c(" A Unicorn     Fish ", "add _cornmeal_", "french fries",
         "ACorn Squash ")

```

which of these strings contains lowercase corn?

```{r}
str_detect(vec, pattern = "Corn")
str_detect(vec, pattern = "corn")
```

Lower and uppercase are different

```{r}

walk_subset <- starwars %>% 
  filter(str_detect(name, pattern = "walk"))

```

using `str_subset()`, kinf of combines filter and str_detect! (Check out key)

### replace a string pattern with something else with `str_replace()`

replace existing string pattern with something else

```{r}

vec_bren <- str_replace(vec, pattern = "corn", replacement = "COOL")
vec_bren

```

replace the pattern "Sky" with "TORNADO"

```{r}

sw_tornado <- starwars %>% 
  mutate(name = str_replace(name, 
                            pattern = "Sky",
                            replacement = "TORNADO"))

```

## Use `str_trim()` to remove excess leading and trailing whitespace

```{r}
vec
str_trim(vec) # get rid of the whitespaces at the end or beginning of the string pattern

```

## `str_squish()`

```{r}

str_squish(vec) # also removes excess whitespace in the middle of words. 

```


```{r}
str_detect(vec, pattern = "CORN")
```

## `str_to_*()`

```{r}
vec
str_to_lower(vec) # most used, more coder friendly
str_to_upper(vec)
str_to_title(vec) 
str_to_sentence(vec) # uppercases the first letter of the word of the string
```

## Using these in combination

```{r}

sw_combo <- starwars %>% 
  filter(str_detect(name, pattern = "Darth")) %>%  # case sensitive though
  mutate(name = str_replace(name, 
                            pattern = "Darth",
                            replacement = "LLAMA")) %>% 
  mutate(name = str_to_lower(name)) # lower case everything in the name column


sw_combo

```




